---
title: "Dominant Resident males cooperate with Satellites to limit their losses"
author: "Belojevis et al."
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MS structure


I. Longitudinal hierarchy analysis BOTH in SATELLITE and in MARGINAL conditions: Lek level hierarchy ~ Session level hierarchy ~ Combo level ~ Combo total level ~ Season level hierarchy (+ In Satellite condition who co-displayed)

Lek rank and satellite cooperation/acceptance/tolerance/rejection (ordinal scale) predict pair formation during/co-display duration the session
  - Co-display (1/0) ~ 
  - Co-display duration ~
  Lek hierarchy effect between co-displaying individuals only on copulation success and behaviour


II. Female baseline

III. Session level

  IIIa. Co-display pattern description (+ Pair formation and terminations between res and sat: courting and attacking satellite and other residents)
  
  IIIb. co-display formation and termination

  IIIc. Session level: Residents within sessions - co-displaying males vs. non-co-displaying ones within session

  1. female visit (nr and duration)
  2. copulations 
  3. display activity/co-display
  4. aggression - is this needed on this level
    towards other residents
    towards satellite partner
    

IV. Combo level: within male analysis between Satellite and Marginal conditions - choose if both or only one
 

- either mean of the week (Method 2) or add days of the week as random (1,2,3 - Method 1)

  1. Copulation nr. 
  2. copulation occurrences
  3. visits nr
  4. duration
  5. Aggression
  6. Display activity/co-display
  
V. combo total level

  - between conditions within a combo
  - between conditions within a specific male
  - between conditions within same ranking individuals


  1. Copulation nr. 
  2. copulation occurrences
  3. visits nr
  4. duration
  5. Aggression
  6. Display activity/co-display
  
  
VI. Season level

  1. Copulation number
  2. Copulation occurrences
  3. Visit nr.
  4. Visit duration
  5. Aggression towards Satellite explains better the sat or the marg hierarchy (in sat cond are successful males less aggressive towards the satellte)
  6. Overall lek attitude score 
  7. Overall display/co-display and copulation relationship between conditions
  
  
+1  Hierarchy steepness in marginal and satellites conditions over the season - to this MS??


### Packages

```{r packages and data set}

library(lme4)
library(lmtest)
library(MASS)
library(glmmTMB)
library(performance)
library(rstanarm)
library(brms)  # for models
library(bayesplot)
library(ggplot2)
library(dplyr)
library(tidybayes)
library(modelr)
library(pscl)
library(GLMMadaptive)
library(fitdistrplus)
library(AER)
library(tidyr)
library(car)
library(AICcmodavg)
library(VGAM) # tobit function
library(DHARMa)
library(readxl)
library(stringr)
library(sjPlot) # ploy_model
library(scales)
library(emmeans)
library(patchwork)
library(data.table)


```



##### Data analysis #####

### II. Female visit/copulation baseline 

## Female baseline data set proeparation

Identifying variables that influences female visits and copulations over the season. Keep the ones with an effect for the later tests.


```{r}
## Number of copulations

Female_baseline <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline.csv")

Female_baseline_res <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline_res.csv")

## Baseline variables: Date2 and Fm_ID - but only based on the zero-inflated model!

# Copulations - using "Total_copulation_nr" for a male that is the total number of successful and interrupted copulations for a session for a male independently from the state - here I use total cop number because I test the female willingness to copulate and not the actual success

hist(Female_baseline$Total_copulation_nr)

hist(Female_baseline_res$Total_copulation_nr)

sum(Female_baseline$Copulation_nr) # 286

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm1"]) # 134

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm2"]) # 152

# Gaussian
fm_cop_bl_lm_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline)
summary(fm_cop_bl_lm_model1)

# Neg bin
fm_cop_bl_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline, family = nbinom2)
summary(fm_cop_bl_nb_model1)
performance::check_zeroinflation(fm_cop_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_nb_model1)
# Ok

fm_cop_bl_poi_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, family = poisson(link="log"), data = Female_baseline)
summary(fm_cop_bl_poi_model1)
performance::check_zeroinflation(fm_cop_bl_poi_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_poi_model1)
# Zero inflated, overdispersed

# Zero-infalted neg bin
fm_cop_bl_zi_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time,, data = Female_baseline, family = nbinom2, zi = ~ Date2 + Fm_ID + Time)
summary(fm_cop_bl_zi_nb_model1)
performance::check_zeroinflation(fm_cop_bl_zi_nb_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_zi_nb_model1)
confint(fm_cop_bl_zi_nb_model1, level = 0.95, method = "profile")
#Ok, final model

anova(fm_cop_bl_nb_model1, fm_cop_bl_zi_nb_model1)

```


# II/b. Visit numbers


```{r Visit number models}

Female_baseline <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline.csv")

### Occurrence of female visits

Female_baseline$Visit_occurrence <- ifelse(Female_baseline$Total_visit_nr_all_females > 0, 1, 0)

log_reg_model <- glm(Visit_occurrence ~ Date2 + Fm_ID + Time, data = Female_baseline, family = binomial)
summary(log_reg_model)

plot_model(log_reg_model, type = "pred", terms = c("Date2", "Fm_ID")) +
  geom_jitter(width = 0, data = Female_baseline, 
             aes(x = Date2, y = Visit_occurrence, color = Fm_ID, group = Fm_ID),
             inherit.aes = FALSE) 
  # scale_x_continuous(expand = c(0, 0)) +
  # scale_y_continuous(labels = percent, limits = c(0, 1)) +
  # labs(x = "Trait Anger", y = "Predicted Probability of Response", title = NULL) +
  theme_light()
  
  
plot_model(log_reg_model, type = "pred", terms = "Date2") +
  geom_jitter(width = 0, data = Female_baseline, 
             aes(x = Date2, y = Visit_occurrence),
             inherit.aes = FALSE) 
  # scale_x_continuous(expand = c(0, 0)) +
  # scale_y_continuous(labels = percent, limits = c(0, 1)) +
  # labs(x = "Trait Anger", y = "Predicted Probability of Response", title = NULL) +
  theme_light()

  
  
### Visit numbers

  sum(Female_baseline$Total_visit_nr_all_females) # 733

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm1"]) # 141

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm2"]) # 592


# Gaussian
fm_vis_bl_lm_model1 <- glmmTMB(Total_visit_nr_all_females ~Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline)
summary(fm_vis_bl_lm_model1)

# Neg bin
fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2)
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# Zero inflated

fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline,  family = nbinom2)
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# Zero inflated, Date2^2 is significant


# Poisson
fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline,  family = poisson(link = "log"))
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# zero inflated, overdispersed


# Zero-inflated neg bin
fm_vis_bl_zinb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2+  Fm_ID + Time + Total_nr_display, data = Female_baseline,  family = nbinom2, zi = ~ 1 ) 
summary(fm_vis_bl_zinb_model1)
performance::check_zeroinflation(fm_vis_bl_zinb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_zinb_model1)
# Zero-inflated Date2^2 is not significant


# Zero-inflated neg bin full model
fm_vis_bl_zinb_model2 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2, zi = ~ 1 + Date2 + Fm_ID + Time) 
summary(fm_vis_bl_zinb_model2)
performance::check_zeroinflation(fm_vis_bl_zinb_model2, tolerance = 0.05)
check_overdispersion(fm_vis_bl_zinb_model2)
confint(fm_vis_bl_zinb_model2, level = 0.95, method = "profile")
# Ok

