---
title: "Dominant Resident males cooperate with Satellites to limit their losses"
author: "Belojevic et al."
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MS structure

### Data and analysis upload is in progress ###


I. Non-social predictors

II. Between Resident differences with a Satellite on the lek 

III. Within-Resident differences between the Satellite and Control conditions 
  


### Packages

```{r packages and data set}

library(lme4)
library(lmtest)
library(MASS)
library(glmmTMB)
library(performance)
library(rstanarm)
library(brms)  # for models
library(bayesplot)
library(ggplot2)
library(dplyr)
library(tidybayes)
library(modelr)
library(pscl)
library(GLMMadaptive)
library(fitdistrplus)
library(AER)
library(tidyr)
library(car)
library(AICcmodavg)
library(VGAM) # tobit function
library(DHARMa)
library(readxl)
library(stringr)
library(sjPlot) # ploy_model
library(scales)
library(emmeans)
library(patchwork)
library(data.table)


```



##### Data analysis #####

### I. Non-social predictors 

# Female baseline data set proeparation

Identifying variables that influences female visits and copulations over the season. Keep the ones with an effect for the later tests.


```{r}
## Number of copulations

Female_baseline <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline.csv")

Female_baseline_res <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline_res.csv")

## Baseline variables: Date2 and Fm_ID - but only based on the zero-inflated model!

# Copulations - using "Total_copulation_nr" for a male that is the total number of successful and interrupted copulations for a session for a male independently from the state - here I use total cop number because I test the female willingness to copulate and not the actual success

hist(Female_baseline$Total_copulation_nr)

hist(Female_baseline_res$Total_copulation_nr)

sum(Female_baseline$Copulation_nr) # 286

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm1"]) # 134

sum(Female_baseline$Copulation_nr[Female_baseline$Fm_ID == "Fm2"]) # 152

# Gaussian
fm_cop_bl_lm_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline)
summary(fm_cop_bl_lm_model1)

# Neg bin
fm_cop_bl_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, data = Female_baseline, family = nbinom2)
summary(fm_cop_bl_nb_model1)
performance::check_zeroinflation(fm_cop_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_nb_model1)
# Ok

fm_cop_bl_poi_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time, family = poisson(link="log"), data = Female_baseline)
summary(fm_cop_bl_poi_model1)
performance::check_zeroinflation(fm_cop_bl_poi_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_poi_model1)
# Zero inflated, overdispersed

# Zero-infalted neg bin
fm_cop_bl_zi_nb_model1 <- glmmTMB(Copulation_nr ~  Date2 + Fm_ID + Time,, data = Female_baseline, family = nbinom2, zi = ~ Date2 + Fm_ID + Time)
summary(fm_cop_bl_zi_nb_model1)
performance::check_zeroinflation(fm_cop_bl_zi_nb_model1, tolerance = 0.05)
check_overdispersion(fm_cop_bl_zi_nb_model1)
confint(fm_cop_bl_zi_nb_model1, level = 0.95, method = "profile")
#Ok, final model

anova(fm_cop_bl_nb_model1, fm_cop_bl_zi_nb_model1)

```


# II/b. Visit numbers


```{r Visit number models}

Female_baseline <- read.csv("Residents benefits ms data analysis Kriszti Jelena/Female_baseline.csv")

### Occurrence of female visits

Female_baseline$Visit_occurrence <- ifelse(Female_baseline$Total_visit_nr_all_females > 0, 1, 0)

log_reg_model <- glm(Visit_occurrence ~ Date2 + Fm_ID + Time, data = Female_baseline, family = binomial)
summary(log_reg_model)

plot_model(log_reg_model, type = "pred", terms = c("Date2", "Fm_ID")) +
  geom_jitter(width = 0, data = Female_baseline, 
             aes(x = Date2, y = Visit_occurrence, color = Fm_ID, group = Fm_ID),
             inherit.aes = FALSE) 
  # scale_x_continuous(expand = c(0, 0)) +
  # scale_y_continuous(labels = percent, limits = c(0, 1)) +
  # labs(x = "Trait Anger", y = "Predicted Probability of Response", title = NULL) +
  theme_light()
  
  
plot_model(log_reg_model, type = "pred", terms = "Date2") +
  geom_jitter(width = 0, data = Female_baseline, 
             aes(x = Date2, y = Visit_occurrence),
             inherit.aes = FALSE) 
  # scale_x_continuous(expand = c(0, 0)) +
  # scale_y_continuous(labels = percent, limits = c(0, 1)) +
  # labs(x = "Trait Anger", y = "Predicted Probability of Response", title = NULL) +
  theme_light()

  
  
### Visit numbers

  sum(Female_baseline$Total_visit_nr_all_females) # 733

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm1"]) # 141

sum(Female_baseline$Total_visit_nr_all_females[Female_baseline$Fm_ID == "Fm2"]) # 592


# Gaussian
fm_vis_bl_lm_model1 <- glmmTMB(Total_visit_nr_all_females ~Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline)
summary(fm_vis_bl_lm_model1)

# Neg bin
fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2)
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# Zero inflated

fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline,  family = nbinom2)
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# Zero inflated, Date2^2 is significant


# Poisson
fm_vis_bl_nb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2 + I(Date2^2) +  Fm_ID + Time, data = Female_baseline,  family = poisson(link = "log"))
summary(fm_vis_bl_nb_model1)
performance::check_zeroinflation(fm_vis_bl_nb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_nb_model1)
# zero inflated, overdispersed


# Zero-inflated neg bin
fm_vis_bl_zinb_model1 <- glmmTMB(Total_visit_nr_all_females ~ Date2+  Fm_ID + Time + Total_nr_display, data = Female_baseline,  family = nbinom2, zi = ~ 1 ) 
summary(fm_vis_bl_zinb_model1)
performance::check_zeroinflation(fm_vis_bl_zinb_model1, tolerance = 0.05)
check_overdispersion(fm_vis_bl_zinb_model1)
# Zero-inflated Date2^2 is not significant


# Zero-inflated neg bin full model
fm_vis_bl_zinb_model2 <- glmmTMB(Total_visit_nr_all_females ~ Date2 +  Fm_ID + Time, data = Female_baseline,  family = nbinom2, zi = ~ 1 + Date2 + Fm_ID + Time) 
summary(fm_vis_bl_zinb_model2)
performance::check_zeroinflation(fm_vis_bl_zinb_model2, tolerance = 0.05)
check_overdispersion(fm_vis_bl_zinb_model2)
confint(fm_vis_bl_zinb_model2, level = 0.95, method = "profile")
# Ok

